Boosted Mirror Descent, Frank-Wolfe, and Herding

### 2013-09-12 icml/paper.tex
added note
fixed proofs in section 3

Mirror descent, together with boosting, yields an algorithm for finding 
``saddle points'' of $L$. It is the following algorithm (called Algorithm 1).
For notational convenience, for a sequence of weights $\alpha_1,\alpha_2,\ldots$ 
let $\hat{u}_t = \frac{\sum_{s=1}^t \alpha_su_s}{\sum_{s=1}^t \alpha_s}$ and let 
$\hat{\theta}_t = \frac{\sum_{s=1}^t \alpha_s\theta_s}{\sum_{s=1}^t \alpha_s}$.
\begin{enumerate}
\item $u_1 \in \arg\min_u h(u)$
\item $\theta_{t} \in \arg\max_{\theta \in \Theta} \langle \theta, u_t \rangle - R(\theta)$
\item $u_{t+1} \in \arg\min_{u} h(u) + \langle \hat{\theta}_t, u \rangle$
%\item $u_{t+1} \in \arg\min_{u} h(u) + \langle \frac{1}{t} \sum_{s \leq t} \theta_s, u \rangle$
\end{enumerate}
As long as $h$ is strongly convex, we obtain the 
bound (see Proposition~\ref{cor:method-1}):
\begin{equation}
\sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq \sup_{\theta \in \Theta} L(u^*, \theta) + O(1/T).
\end{equation}
In other words, $\hat{u}_T$ is close to being a global minimum of $L$.
However, it is often the case that $h$ is not strongly convex, whereas $R$ is strongly convex. In this case 
we may wish to use the following slightly different algorithm (called Algorithm 2):
\begin{enumerate}
\item $\theta_1 \in \arg\min_{\theta} R(\theta)$
\item $u_t \in \arg\min_{u} h(u) + \langle \theta_t, u \rangle$
%\item $\theta_{t+1} \in \arg\max_{\theta \in \Theta} \langle \theta, \frac{1}{t} \sum_{s \leq t} u_s \rangle - R(\theta)$
\item $\theta_{t+1} \in \arg\max_{\theta \in \Theta} \langle \theta, \hat{u}_t \rangle - R(\theta)$
\end{enumerate}
We then obtain the following bound 
when $R$ is strongly convex (see Proposition~\ref{cor:method-2}):
\[ \sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq \sup_{\theta \in \Theta} L(u^*, \theta) + O(1/T). \]
Algorithm 1 and Algorithm 2 are closely related; indeed, they are dual to each other 
(performing Algorithm 1 on $L(u,\theta)$ is the same as performing Algorithm 2 on 
$-L(\theta,u)$).
\NA{JHH: It would be more elegant to argue either here or below that the bounds on the second algorithm follow directly from duality}

\section{Convergence Proofs}
\label{sec:proofs}
We now prove the convergence results cited in Section~\ref{sec:algorithm}. 
We start with two preliminary lemmas.
\label{lem:ftl}
Let $l_1,\ldots,l_T$ be functions of $x$ and let $x_1,\ldots,x_T$ 
be chosen via $x_{t+1} \in \arg\min_{x} \frac{1}{t} \sum_{s \leq t} l_s(x)$. 
Then for any $x^*$ we have
\[ \sum_{t=1}^T l_t(x_t) \leq \sum_{t=1}^T l_t(x^*) + \sum_{t=1}^T (l_t(x_t) - l_t(x_{t+1})). \]
\NA{JHH: Doesn't rely on the spaces $x$'s having any structure nor on any properties of the functions.}
Re-arranging, we want to show that $\sum_{t=1}^T l_t(x_{t+1}) \leq \sum_{t=1}^T l_t(x^*)$ for 
all $x^*$. We will show this by induction. In the base case $T=1$, we want to show that $l_1(x_2) \leq l_1(x^*)$ 
for all $x^*$, which is true because $x_2 \in \argmin_x l_1(x)$ by construction. For 
the inductive step, suppose that the result holds for $T-1$:
\[ \sum_{t=1}^{T-1} l_t(x_{t+1}) \leq \sum_{t=1}^T l_t(x^*). \]
Now set $x^* = x_{T+1}$ in the above inequality and 
add $l_T(x_{T+1})$ to both sides to get
\sum_{t=1}^T l_t(x_{t+1}) &\leq \sum_{t=1}^T l_t(x_{T+1}) \\
 &= \min_{x} \sum_{t=1}^T l_t(x) \\
 &\leq \sum_{t=1}^T l_t(x^*),
which completes the induction. Here we are using the fact that $x_{T+1}$ 
is the minimizer of $\frac{1}{T} \sum_{t=1}^T l_t(x)$ and hence also of 
$\sum_{t=1}^T l_t(x)$.

@@

@@

Suppose that $f(x)$ is \emph{$\alpha$-strongly convex}: $f(x) \geq f(x_0) + \partial f(x_0)^T(x-x_0) + \frac{\alpha}{2}\|x-x_0\|^2$. 
Let $F(y) := \arg\min_x f(x) + y^Tx$. Then $\|F(y_0)-F(y_1)\| \leq \frac{2}{\alpha} \|y_0-y_1\|$.

@@

\NA{JHH: Follows from $f$ being strongly convex, the definition of inner product, and Cauchy-Schwartz. We'll just want to be careful about calculating $\alpha$ for our regularizer later on.}
Let $x_0 = F(y_0)$. Then we must have $\partial f(x_0) = -y_0$, hence 
f(x)+y_1^Tx &\geq f(x_0) + y_1^Tx_0 - y_0^T(x-x_0) + \frac{\alpha}{2}\|x-x_0\|^2.
But any minimizer of $f(x) + y_1^Tx$ must at least have a value less than $f(x_0) + y_1^Tx_0$. 
         & y_1^Tx_0 \geq y_1^Tx_1 - y_0^T(x_1-x_0) + \frac{\alpha}{2}\|x_1-x_0\|^2 \\
\implies & (y_1-y_0)^T(x_0-x_1) \geq \frac{\alpha}{2}\|x_1-x_0\|^2 \\
\implies & \|y_1-y_0\|\|x_0-x_1\| \geq \frac{\alpha}{2}\|x_1-x_0\|^2 \\
\implies & \|x_1-x_0\| \leq \frac{2}{\alpha} \|y_1-y_0\|,

@@

\[ \sup_{\theta} L(\hat{u}_T, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{\sum_{t=1}^T \alpha_t \langle u_t - u_{t+1}, \theta_t \rangle}{\sum_{t=1}^T \alpha_t}. \]

@@

\NA{JHH: Uses, Lemma~\ref{lem:ftl}, convexity of $h$, taking supremums, and facts that follow from the construction of the algorithm.}
Note that $L(u_t, \theta_t) = \max_{\theta} L(u_t, \theta)$ by construction. Also note that, if we invoke 
Lemma~\ref{lem:ftl} with $l_t(u) = \alpha_t L(u, \theta_t)$, then we get the inequality
\[ \sum_{t=1}^T \alpha_t L(u_t, \theta_t) \leq \sum_{t=1}^T \alpha_t L(u^*, \theta_t) + \sum_{t=1}^T \alpha_t \langle u_t - u_{t+1}, \theta_t \rangle. \]

@@

L(\hat{u}_T, \theta) &= L\left(\frac{\sum_{t=1}^T \alpha_tu_t}{\sum_{t=1}^T \alpha_t}, \theta\right) \\
 &\leq \frac{\sum_{t=1}^T \alpha_t L(u_t, \theta)}{\sum_{t=1}^T \alpha_t} \\
 &\leq \frac{\sum_{t=1}^T \alpha_t L(u_t, \theta_t)}{\sum_{t=1}^T \alpha_t} \\
 &\leq \frac{\sum_{t=1}^T \alpha_tL(u^*, \theta_t)}{\sum_{t=1}^T \alpha_t} \\ &\phantom{=} + \frac{\sum_{t=1}^T \alpha_t (L(u_t,\theta_t)-L(u_{t+1},\theta_t))}{\sum_{t=1}^T \alpha_t} \\
 &= L(u^*, \theta_t) + \frac{\sum_{t=1}^T \alpha_t \langle u_t - u_{t+1}, \theta_t \rangle)}{\sum_{t=1}^T \alpha_t} \\ &\phantom{=} + \frac{\sum_{t=1}^{T} \alpha_t(h(u_t)-h(u_{t+1}))}{\sum_{t=1}^T \alpha_t} \\
 &= L(u^*, \theta_t) + \frac{\sum_{t=1}^T \alpha_t \langle u_t - u_{t+1}, \theta_t \rangle}{\sum_{t=1}^T \alpha_t} \\ &\phantom{=} + \frac{\alpha_1 h(u_1) - \alpha_T h(u_{T+1}) + \sum_{t=2}^{T} (\alpha_t-\alpha_{t-1}) h(u_t)}{\sum_{t=1}^T \alpha_t} \\
 &\leq L(u^*, \theta_t) + \frac{\sum_{t=1}^T \alpha_t \langle u_t - u_{t+1}, \theta_t \rangle}{\sum_{t=1}^T \alpha_t} \\
 &\leq \sup_{\theta} L(u^*, \theta) + \frac{\sum_{t=1}^T \alpha_t \langle u_t - u_{t+1}, \theta_t \rangle}{\sum_{t=1}^T \alpha_t},

@@

Suppose that $h$ is $\gamma$-strongly convex and let $r = \sup_{\theta} |\langle \theta, \theta \rangle|_2$. Then 
\[ \sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{16r^2}{\gamma T^2}. \]

@@

\NA{JHH: Follows from Lemma~\ref{lem:convexity}, triangle inequality, taking supremums, and Cauchy-Schwartz.}

@@

\|u_t-u_{t+1}\| &\leq \frac{2}{\gamma}\|\frac{\sum_{s \leq t}\alpha_s\theta_s}{\sum_{s \leq t} \alpha_s} - \frac{\sum_{s \leq t+1}\alpha_s\theta_s}{\sum_{s \leq t+1} \alpha_s}\| \\
 &= \frac{2}{\gamma}\|\frac{\alpha_{t+1}}{A_tA_{t+1}} \sum_{s \leq t} \alpha_s\theta_s - \frac{\alpha_{t+1}}{A_{t+1}} \theta_{t+1}\| \\
 &\leq \frac{2}{\gamma} \left(\frac{\alpha_{t+1}}{A_tA_{t+1}} \sum_{s \leq t} \alpha_s\|\theta_s\| + \frac{\alpha_{t+1}}{A_{t+1}} \|\theta_{t+1}\|\right) \\
 &\leq \frac{4r\alpha_{t+1}}{\gamma A_{t+1}}.

@@

It follows from Cauchy-Schwartz that 

@@

\frac{1}{A_T} \sum_{t=1}^T \alpha_t \langle u_t - u_{t+1}, \theta_t \rangle &\leq \sum_{t=1}^T \frac{4r^2\alpha_{t}\alpha_{t+1}}{\gamma A_{t+1}A_T} \\
 &\leq \frac{4r^2}{\gamma A_T} \sum_{t=1}^T \frac{\alpha_{t}\alpha_{t+1}}{A_{t+1}}.

@@

In particular, if we let $\alpha_t = t$, then $A_t = \frac{t(t+1)}{2}$ and $\frac{\alpha_{t}\alpha_{t+1}}{A_{t+1}} = 2$. 

@@

\frac{1}{A_T} \sum_{t=1}^T \alpha_t\langle u_t-u_{t+1}, \theta_t \rangle \leq \frac{16r^2}{T(T+1)},

@@

and $\theta_{t+1} \in \arg\max_{\theta} \langle \theta, \frac{1}{t} \sum_{s \leq t} u_s \rangle - R(\theta)$. 
Then for $\hat{u} = \frac{1}{T} \sum_{t=1}^T u_t$, we have 
\[ \sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{1}{T} \sum_{t=1}^T \langle u_t, \theta_{t+1} - \theta_{t} \rangle. \]

@@

If we invoke Lemma~\ref{lem:ftl} with $l_t(\theta) = -L(u_t, \theta)$, then we get the inequality
\[ \sum_{t=1}^T -L(u_t, \theta_t) \leq -\sum_{t=1}^T L(u_t, \theta^*) - \sum_{t=1}^T \langle u_t, \theta_t - \theta_{t+1} \rangle. \]

@@

\[ \sum_{t=1}^T L(u_t, \theta^*) \leq \sum_{t=1}^T L(u_t, \theta_t) + \sum_{t=1}^T \langle u_t, \theta_{t+1} - \theta_t \rangle. \]

@@

L(\hat{u}, \theta) &= L\left(\frac{1}{T} \sum_{t=1}^T u_t, \theta\right) \\
 &\leq \frac{1}{T} \sum_{t=1}^T L(u_t, \theta) \\
 &\leq \frac{1}{T} \sum_{t=1}^T L(u_t, \theta_t) + \frac{1}{T} \sum_{t=1}^T \langle u_t, \theta_{t+1} - \theta_t \rangle \\
 &= \frac{1}{T} \sum_{t=1}^T \inf_{u} L(u, \theta_t) + \frac{1}{T} \sum_{t=1}^T \langle u_t, \theta_{t+1} - \theta_t \rangle \\
 &\leq \frac{1}{T} \sum_{t=1}^T L(u^*, \theta_t) + \frac{1}{T} \sum_{t=1}^T \langle u_t, \theta_{t+1} - \theta_t \rangle \\
 &\leq \frac{1}{T} \sum_{t=1}^T \sup_{\theta} L(u^*, \theta) + \frac{1}{T} \sum_{t=1}^T \langle u_t, \theta_{t+1} - \theta_t \rangle \\
 &= \sup_{\theta} L(u^*, \theta) + \frac{1}{T} \sum_{t=1}^T \langle u_t, \theta_{t+1} - \theta_t \rangle,

@@

Suppose that $R$ is $\gamma$-strongly convex and let $r = \sup_{u} |\langle u, u \rangle|$. Then
\[ \sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{16r^2}{\gamma T^2}. \]

>>>>

Mirror descent, together with boosting, yields an algorithm for finding 
``saddle points'' of $L$. It is the following algorithm (called Algorithm 1).
For notational convenience, for a sequence of weights $\alpha_1,\alpha_2,\ldots$ 
let $\hat{u}_t = \frac{\sum_{s=1}^t \alpha_su_s}{\sum_{s=1}^t \alpha_s}$ and let 
$\hat{\theta}_t = \frac{\sum_{s=1}^t \alpha_s\theta_s}{\sum_{s=1}^t \alpha_s}$.
\begin{enumerate}
\item $u_1 \in \arg\min_u h(u)$
\item $\theta_{t} \in \arg\max_{\theta \in \Theta} \langle \theta, u_t \rangle - R(\theta)$
\item $u_{t+1} \in \arg\min_{u} h(u) + \langle \hat{\theta}_t, u \rangle$
%\item $u_{t+1} \in \arg\min_{u} h(u) + \langle \frac{1}{t} \sum_{s \leq t} \theta_s, u \rangle$
\end{enumerate}
As long as $h$ is strongly convex, we obtain the 
bound (see Proposition~\ref{cor:method-1}):
\begin{equation}
\sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq \sup_{\theta \in \Theta} L(u^*, \theta) + O(1/T).
\end{equation}
In other words, $\hat{u}_T$ is close to being a global minimum of $L$.
However, it is often the case that $h$ is not strongly convex, whereas $R$ is strongly convex. In this case 
we may wish to use the following slightly different algorithm (called Algorithm 2):
\begin{enumerate}
\item $\theta_1 \in \arg\min_{\theta} R(\theta)$
\item $u_t \in \arg\min_{u} h(u) + \langle \theta_t, u \rangle$
%\item $\theta_{t+1} \in \arg\max_{\theta \in \Theta} \langle \theta, \frac{1}{t} \sum_{s \leq t} u_s \rangle - R(\theta)$
\item $\theta_{t+1} \in \arg\max_{\theta \in \Theta} \langle \theta, \hat{u}_t \rangle - R(\theta)$
\end{enumerate}
We then obtain the following bound 
when $R$ is strongly convex (see Proposition~\ref{cor:method-2}):
\[ \sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq \sup_{\theta \in \Theta} L(u^*, \theta) + O(1/T). \]
Algorithm 1 and Algorithm 2 are closely related; indeed, they are dual to each other 
(performing Algorithm 1 on $L(u,\theta)$ is the same as performing Algorithm 2 on 
$-L(\theta,u)$).
\NA{JHH: It would be more elegant to argue either here or below that the bounds on the second algorithm follow directly from duality}
\NA{JNS: The statements aren't actually dual to each other; the first is saying that the primal converges to its 
    optimum, and the second is saying that the dual converges to its optimum.}

\section{Convergence Proofs}
\label{sec:proofs}
We now prove the convergence results cited in Section~\ref{sec:algorithm}. 
Throughout this section, assume that $\alpha_1,\ldots,\alpha_T$ is 
a sequence of real numbers and that $A_t = \sum_{s=1}^t \alpha_s$. 
We further require that $A_t \geq 0$ for all $t$.

Also recall that the Bregman divergence is defined by 
$D_f(x_2 \| x_1) \eqdef f(x_2) - \langle \nabla f(x_1), x_2-x_1 \rangle - f(x_1)$.

Our proofs hinge on the following key lemma:
\begin{lemma}
\label{lem:bregman}
Let $z_1,\ldots,z_T$ be vectors and let $f(x)$ be a strictly convex 
function. Define $\hat{z}_t$ to be $\frac{1}{A_t} \sum_{s=1}^t \alpha_s z_s$.

Let $x_1,\ldots,x_T$ be chosen via $x_{t+1} = \arg\min_{x} f(x) + \langle \hat{z}_t, x\rangle$. 
Then for any $x^*$ we have
\begin{align*}
\lefteqn{\frac{1}{A_T} \sum_{t=1}^T \{\alpha_t(f(x_t) + \langle z_t, x_t \rangle)\}} \\
\phantom{+} &\leq f(x^*) + \langle \hat{z}_t, x^* \rangle + \frac{1}{A_T} \sum_{t=1}^T A_t D_{f}(x_t \| x_{t+1}). 
\end{align*}
\end{lemma}
\begin{proof}
First note that, if $x_0 = \arg\min f(x) + \langle z, x \rangle$, 
then $\nabla f(x_0) = -z$.

\NA{JNS: In the following proof, (2) is by the update formula for $x_{t+1}$ together with the preceding observation.  (3) is applying (2). (4) and (5) are re-arranging the sum. (6) is definition of Bregman divergence. (7) is the observation again. 
(8) is the definition of $x_{T+1}$.}

Now note that
\begin{align}
\alpha_{t}z_{t} = A_{t}\hat z_{t} - A_{t-1}\hat z_{t-1} = - A_{t}\nabla f(x_{t+1}) + A_{t-1} \nabla f(x_{t}) 
\end{align}
so we have
\begin{align}
\lefteqn{\sum_{t=1}^T \{\alpha_t(f(x_t) + \langle z_t, x_t \rangle)\}} \\
 &= \sum_{t=1}^T \{\alpha_t f(x_t) + \langle A_{t-1} \nabla f(x_t) - A_t \nabla f(x_{t+1}), x_t \rangle\} \\
 &= \sum_{t=1}^T \{\alpha_t f(x_t) - \langle A_{t} \nabla f(x_{t+1}), x_t-x_{t+1} \rangle\} - A_{T}\langle \nabla f(x_{T+1}), x_{T+1} \rangle \\
 &= \sum_{t=1}^T \{A_t f(x_t) - \langle A_{t} \nabla f(x_{t+1}), x_t-x_{t+1} \rangle - A_t f(x_{t+1})\}  \\
 &\quad+ A_T(f(x_{T+1}) - \langle \nabla f(x_{T+1}), x_{T+1} \rangle) \nonumber \\
 &= \sum_{t=1}^T \{A_tD_f(x_t \| x_{t+1})\} + A_T(f(x_{T+1}) - \langle \nabla f(x_{T+1}), x_{T+1} \rangle) \\
 &= \sum_{t=1}^T \{A_tD_f(x_t \| x_{t+1})\} + A_T(f(x_{T+1}) + \langle \hat{z}_T, x_{T+1} \rangle) \\
 &\leq \sum_{t=1}^T \{A_tD_f(x_t \| x_{t+1})\} + A_T(f(x^*) + \langle \hat{z}_T, x^* \rangle). \\
\end{align}
Dividing both sides by $A_T$ completes the proof.

@@

We also note that $D_f(x_t \| x_{t+1}) = D_{f^*}(\hat{z}_{t+1} \| z_t)$, where $f^*(z) = \sup_x \langle z,x\rangle - f(x)$. 
This form of the bound will often be more useful to us.

@@

Suppose that $D_f(x' \| x) \geq \frac{1}{2}\|x-x'\|^2$ for some 
norm $\|\cdot\|$. (In this case we say that $f$ is strongly 
convex with respect to $\|\cdot\|$.) 
Then $D_{f^*}(x' \| x) \leq \frac{1}{2}\|x-x'\|_{*}^2$.

@@

@@

\sup_{\theta} L(\hat{u}_T, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{1}{A_T} \sum_{t=1}^T A_tD_f(x_t \| x_{t+1}).

@@

Note that $L(u_t, \theta_t) = \max_{\theta} L(u_t, \theta)$ by construction. 
Also note that, if we invoke Lemma~\ref{lem:bregman} with $f = h$ and 
$z_t = \theta_t$, then we get the inequality
\frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u_t, \theta_t) \leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u^*, \theta_t) + \frac{1}{A_T} \sum_{t=1}^T A_tD_f(x_t \| x_{t+1}).

@@

L(\hat{u}_T, \theta) &= L\left(\frac{1}{A_T} \sum_{t=1}^T \alpha_tu_t, \theta\right) \\
 &\leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u_t, \theta) \\
 &\leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u_t, \theta_t) \\
 &\leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u^*, \theta_t) + \frac{1}{A_T} \sum_{t=1}^T A_t D_f(u_t \| u_{t+1}) \\
 &\leq \sup_{\theta} L(u^*, \theta) + \frac{1}{A_T} \sum_{t=1}^T A_tD_f(u_t \| u_{t+1}),

@@

Suppose that $h$ is strongly convex with respect to a norm $\|\cdot\|$ 
and let $r = \sup_{\theta} \|\theta\|_{*}$. Then 
\[ \sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{2r^2}{A_T} \sum_{t=1}^T \frac{\alpha_{t+1}^2A_t}{A_{t+1}^2}. \]
In particular, for $\alpha_t = t$, we have
\[ \sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{8r^2}{T^2}. \]

@@

@@

D_f(x_t \| x_{t+1}) &= D_{f^*}(\hat{\theta}_{t+1} \| \hat{\theta}) \\
 &\leq \frac{1}{2}\|\theta_{t+1}-\theta\|_{*}^2 \\
 &= \frac{1}{2}\|\frac{\sum_{s \leq t}\alpha_s\theta_s}{\sum_{s \leq t} \alpha_s} - \frac{\sum_{s \leq t+1}\alpha_s\theta_s}{\sum_{s \leq t+1} \alpha_s}\|_{*}^2 \\
 &= \frac{1}{2}\|\frac{\alpha_{t+1}}{A_tA_{t+1}} \sum_{s \leq t} \alpha_s\theta_s - \frac{\alpha_{t+1}}{A_{t+1}} \theta_{t+1}\|_{*}^2 \\
 &\leq \frac{1}{2} \left(\frac{\alpha_{t+1}}{A_tA_{t+1}} \sum_{s \leq t} \alpha_s\|\theta_s\|_{*}^2 + \frac{\alpha_{t+1}}{A_{t+1}} \|\theta_{t+1}\|_{*}^2\right)^2 \\
 &\leq \frac{2r^2\alpha_{t+1}^2}{A_{t+1}^2}.

@@

@@

\frac{1}{A_T} \sum_{t=1}^T A_tD_f(x_t \| x_{t+1}) &\leq \frac{2r^2}{A_T} \sum_{t=1}^T \frac{\alpha_{t+1}^2A_t}{A_{t+1}^2}.

@@

In particular, if we let $\alpha_t = t$, then $A_t = \frac{t(t+1)}{2}$ and 
$\frac{\alpha_{t+1}^2A_t}{A_{t+1}^2} = \frac{2(t+1)^2t(t+1)}{(t+1)^2(t+2)^2} = \frac{2t(t+1)}{(t+2)^2} \leq 2$.

@@

\frac{2r^2}{A_T} \sum_{t=1}^T \frac{\alpha_{t+1}^2A_t}{A_{t+1}^2} \leq \frac{8r^2}{T(T+1)},

@@

and $\theta_{t+1} \in \arg\max_{\theta} \langle \theta, \hat{u}_t \rangle - R(\theta)$. 
\sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{1}{A_T} \sum_{t=1}^T A_tD_{R}(\theta_t \| \theta_{t+1}).

@@

If we invoke Lemma~\ref{lem:bregman} with $f=R$ and $z_t=-u_t$, then we get 
the inequality
\[ \frac{1}{A_T} \sum_{t=1}^T -\alpha_t L(u_t, \theta_t) \leq \frac{1}{A_T} \sum_{t=1}^T -\alpha_t L(u_t, \theta^*) - \frac{1}{A_T} \sum_{t=1}^T A_tD_R(\theta_t \| \theta_{t+1}). \]

@@

\[ \frac{1}{A_T }\sum_{t=1}^T \alpha_t L(u_t, \theta^*) \leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u_t, \theta_t) + \frac{1}{A_T} \sum_{t=1}^T A_tD_R(\theta_t \| \theta_{t+1}). \]

@@

L(\hat{u}, \theta) &= L\left(\frac{1}{A_T} \sum_{t=1}^T \alpha_t u_t, \theta\right) \\
 &\leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u_t, \theta) \\
 &\leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u_t, \theta_t) + \frac{1}{A_T} \sum_{t=1}^T A_t D_R(\theta_t \| \theta_{t+1}) \\
 &= \frac{1}{A_T} \sum_{t=1}^T \alpha_t \inf_{u} L(u, \theta_t) + \frac{1}{A_T} \sum_{t=1}^T A_tD_R(\theta_t \| \theta_{t+1}) \\
 &\leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t L(u^*, \theta_t) + \frac{1}{A_T} \sum_{t=1}^T A_tD_R(\theta_t \| \theta_{t+1}) \\
 &\leq \frac{1}{A_T} \sum_{t=1}^T \alpha_t \sup_{\theta} L(u^*, \theta) + \frac{1}{A_T} \sum_{t=1}^T A_tD_R(\theta_t \| \theta_{t+1}) \\
 &= \sup_{\theta} L(u^*, \theta) + \frac{1}{A_T} \sum_{t=1}^T A_tD_R(\theta_t \| \theta_{t+1}),

@@

Suppose that $R$ is strongly convex with respect to a norm $\|\cdot\|$ 
and let $r = \sup_{u} \|u\|_{*}$. Then 
\[ \sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{2r^2}{A_T} \sum_{t=1}^T \frac{\alpha_{t+1}^2A_t}{A_{t+1}^2}. \]
In particular, for $\alpha_t = t$, we have
\[ \sup_{\theta} L(\hat{u}, \theta) \leq \sup_{\theta} L(u^*, \theta) + \frac{8r^2}{T^2}. \]
